---
title: "Classify Sonar Targets between Mines and Rocks Using FFTrees"
output:
  html_document:
    df_print: paged
    number_sections: true
---

# Sonar data
A data frame with 208 observations on 61 variables. The variables V1-V60 represent the energy within a certain frequency band, and are to be used as predictors. The variable 'mine.crit' is a class label, FALSE for 'rock' (97 observations) and TRUE for 'mine' (111 observations).

## Reference
Gorman, R. P., and Sejnowski, T. J. (1988). "Analysis of Hidden Units in a Layered Network Trained to Classify Sonar Targets" in Neural Networks, Vol. 1, pp. 75-89.

# Classify Sonar Targets between Mines and Rocks Using FFTrees
[FFTrees](https://github.com/ndphillips/FFTrees) is an R package to create and visualize fast-and-frugal decision trees (FFTs)

## Load sonar data
```{r load sonar data, echo=FALSE, message=FALSE}
library(FFTrees)
sonar
```

## Set FFTrees
```{r}
# Create FFTs from the sonar data
set.seed(100) # For replicability of the training / test data split
sonar.fft <- FFTrees(formula = mine.crit ~.,
                         data = sonar,
                         train.p = 1,      # Split data into 50\50 training \ test
                         main = "Sonar",
                         decision.labels = c("Rock", "Mine"))  
```

## Classification results
### Training accuracies
```{r}
# look at the individual cue training accuracies:
plot(sonar.fft, 
     what = "cues")
```

### Best tree
```{r}
# plot the best tree
plot(sonar.fft)
#plot(sonar.fft, tree=3)
```

### Predict classes of test data
```{r}
sonar.fft.pred <- predict(sonar.fft, newdata=sonar)
head(sonar.fft.pred)
```

### Predict class probabilities
```{r}
sonar.fft.pred <- predict(sonar.fft, newdata=sonar[1:15, ],
                             type = "prob")
head(sonar.fft.pred)
```


                            